PERs from Partial Projections for Higher-order Polymorphic Demand Analysis

### 2017-05-01 pubs/demand_analysis/new.verb.tex
sync before branch

\begin{abstract}
  {\it First-order\/} projection-based strictness analysis (generally,
  \emph{demand analysis}) was first introduced by Wadler and Hughes in
  1987~\cite{WH87}.  This development was restricted to first-order,
  monomorphic languages and provided no proof of soundness.  Subsequent
  developments extended the theory to other analyses (most notably
  binding-time analysis), approaches to higher order, and polymorphism.  Yet
  other developments were based on generalization of projections, specifically
  partial equivalence relations and partial projections, the latter notably
  simplifying a difficulty with projection-based strictness analysis dating
  back to Wadler and Hughes.  However, to date no development has combined the
  desirable attributes of all of these approaches.  We present the first
  practical, higher-order, polymorphic,
  partial-projection/partial-equivalence-relation based demand analysis,
  together with a proof of satisfaction of the fundamental safety condition
  for such analyses.  Such an analysis can be used both to improve serial code
  generation as well as enable safe automatic parallelization for lazy or
  non-strict functional languages.

>>>>

\begin{abstract}
  {\it First-order\/} projection-based strictness analysis (generally,
  \emph{demand analysis}) was first introduced by Wadler and Hughes in
  1987~\cite{WH87}.  This development was restricted to first-order,
  monomorphic languages and provided no proof of soundness.  Subsequent
  developments extended the theory to other analyses (most notably
  binding-time analysis), approaches to higher order, and polymorphism.  Yet
  other developments were based on generalization of projections, specifically
  partial equivalence relations and partial projections, the latter notably
  smoothing over a complicating construction in projection-based strictness
  analysis dating back to Wadler and Hughes.  However, to date no development
  has combined the desirable attributes of all of these approaches, or given
  the details where unboxed types are explicit.  We present the first
  practical, higher-order, polymorphic, forward demand analysis based on
  partial projections, incorporating the notions of partial equivalence
  relations and logical relations, together with a proof of satisfaction of
  the fundamental correctness condition for such analyses.  Such an analysis
  can be used both to improve serial code generation, as well as enable safe
  automatic parallelization, for lazy or non-strict functional languages.
